---
title: "Lab02"
author: "Brian Sayre, Justin Park, and Desmond Orton"
date: "2/17/2021"
output: html_document
---

<h1>Question 1</h1>
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

```{r}
library('ggplot2')
head(choco)
```
```{r}
hist(choco$Rating)
```
```{r}
boxplot(choco$Rating)
```

<h1>Question 2</h1>
```{r}
t <- table(choco$Location)
barplot(t)
```

<h1>Question 3</h1>

```{r}
correlation <- cor(choco$Cocoa_Percent, choco$Rating)
correlation

#For this we took the average rating and grouped it by the cocoa_percent
#Without modifying the data how we did the plot would give useless data of dots in lines.
agg1 = aggregate(choco$Rating, by=list(choco$Cocoa_Percent), FUN=mean)
agg1

plot(agg1)

#For this we did the same as above but in reverse
agg2 = aggregate(choco$Cocoa_Percent, by=list(choco$Rating), FUN=mean)
agg2

plot(agg2)
``` 

<h1>Question 4</h1>
#Average Ratings by Origin Country
origins <- aggregate(choco$Rating, by=list(choco$Bean_Origin), FUN=mean)
plot(origins$x, xlab = "Countries", ylab = "Average Ratings")

<h1>Question 5</h1>
```{r}
#Cocoa Percent by Company
agg3 = aggregate(choco$Cocoa_Percent, by=list(choco$Company), FUN=length)
head(agg3, 10)

pie(unique(choco$Cocoa_Percent))
```

### Characteristics

In this section we took a look at how characteristic 1 of the chocolate affected the rating of the chocolate. Then, we looked at where the beans' origin was with those most common characteristics. 
```{r}
t <- table(choco$Characteristics1)
charDF <- as.data.frame(t) 
tail(charDF, 3)
data <- charDF[order(charDF$Freq),]
tail(data, 3)
```
This is showing us the most common characteristics for the chocolates. Next, we look at just the ratings with those ratings.

```{r}
creamy <- choco[choco$Characteristics1 == "creamy",]
creamyMean <- mean(creamy$Rating)
print(creamyMean)
loc <- table(creamy$Bean_Origin)
locDF <- as.data.frame(loc) 
data <- locDF[order(locDF$Freq),]
tail(data, 3)
```
Here is the average rating for chocolates, 3.484568, with the creamy characteristic, which is a higher mean than most other characteristics. Also, we can see that most beans with the creamy characteristic come from Venezuela. 

```{r}
sandy <- choco[choco$Characteristics1 == "sandy",]
sandyMean <- mean(sandy$Rating)
print(sandyMean)
loc <- table(sandy$Bean_Origin)
locDF <- as.data.frame(loc) 
data <- locDF[order(locDF$Freq),]
tail(data, 3)
```
Here is the average rating for chocolates, 3.091418, with the sandy characteristic. Also, we can see that most beans with the sandy characteristic come from Peru. 

```{r}
intense <- choco[choco$Characteristics1 == "intense",]
intenseMean <- mean(intense$Rating)
print(intenseMean)
loc <- table(intense$Bean_Origin)
locDF <- as.data.frame(loc) 
data <- locDF[order(locDF$Freq),]
tail(data, 3)
```
Here is the average rating for chocolates, 3.207317, with the sandy characteristic. Also, we can see that most beans with the intense characteristic come from Venezuela. 
